Dissertation

### 2024-06-21 index.qmd
update home page

---
title: "Dissertation"
author: Thomas E. Gorman
comments: false
date-format: 'MMM YYYY'
format:
  html:
    grid:
      sidebar-width: 250px
      body-width: 1400px
      margin-width: 170px
      gutter-width: 1.5rem
    self-contained: false
---

@@

@@

@@

>>>>

---
title: "Dissertation"
author:
- name: Thomas E. Gorman
  affiliation: Indiana University
  affiliation-url: https://psych.indiana.edu/
  url: https://tegorman13.github.io/
  orcid: 0000-0001-5366-5442
comments: false
date-format: 'MMM YYYY'
format:
  html:
    grid:
      sidebar-width: 250px
      body-width: 1400px
      margin-width: 170px
      gutter-width: 1.5rem
    self-contained: false
---

@@

[{{< fa brands github >}} repo](https://github.com/tegorman13/IGAS_Variability) \

@@

[{{< fa brands github >}} repo](https://github.com/tegorman13/htw) \

@@

[{{< fa brands github >}} repo](https://github.com/tegorman13/Dissertation) \
